nuclear energy in comparison

### 2024-01-15 nuclear in comparison.Rmd
commiting after a long time. oh god

---
title: 'nuclear energy in comparison'
output:
  pdf_document:
    toc: yes
    toc_depth: 2
    keep_tex: yes
  header-includes:
  - \usepackage{dcolumn}
  - \usepackage{array}
  keep_md: yes
---

@@

\newpage
# State Specific Differences.

@@

@@

```{r}
staterisky <- joineddf %>%
  dplyr::select(!starts_with(c("Ben_IND", "Risky_IND")))%>%
  dplyr::select(starts_with("Risky"), State)

@@

str(staterisky_mean)

# Load required packages
library(dplyr)
library(tidyr)
library(ggplot2)

@@

# Order Technologies
technology_order <- c("Nuclear", "Gas", "Coal", "Oil", "Hydro", "Wind", "Solar")
long_data$Technology <- factor(long_data$Technology, levels = technology_order)

# Plot the graph
ggplot(long_data, aes(x = Technology, y = Mean_Score, color = State, group = State)) +
  geom_line(size = 1) +
  geom_point(size = 3) +
  labs(title = "Mean Perceived Risk by State",
       x = "Technology", y = "Mean Score") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

@@

```{r}
# Using dplyr and tidyr

standardized_data <- long_data %>%
  group_by(Technology) %>%
  mutate(
    Overall_Mean = mean(Mean_Score, na.rm = TRUE),
    Std_Dev = sd(Mean_Score, na.rm = TRUE)
  ) %>%
  ungroup() %>%
  mutate(Standardized_Score = (Mean_Score - Overall_Mean) / Std_Dev) %>%
  dplyr::select(-Overall_Mean, -Std_Dev)  #

# Order Technologies
technology_order <- c("Nuclear", "Gas", "Coal", "Oil", "Hydro", "Wind", "Solar")
standardized_data$Technology <- factor(standardized_data$Technology, levels = technology_order)

# Plot the graph
ggplot(standardized_data, aes(x = Technology, y = Standardized_Score, color = State, group = State)) +
  geom_line(size = 1) +
  geom_point(size = 3) +
  labs(title = "Standardised Scores of Technologies by State",
       x = "Technology", y = "Z Score") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

@@

```{r}
# Switch roles of State and Technology for plotting
ggplot(standardized_data, aes(x = State, y = Standardized_Score, color = Technology, group = Technology)) +
  geom_line(size = 1) +
  geom_point(size = 3) +
  labs(title = "Standardised Scores of Technologies by State",
       x = "State", y = "Z Score") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

>>>>

---
title: "nuclear energy in comparison"
output:
  pdf_document:
    toc: yes
    toc_depth: 2
    keep_tex: yes
    keep_md: yes
  header-includes:
  - \usepackage{dcolumn}
  - \usepackage{array}
  - \usepackage{pdflscape}
  - \newcommand{\blandscape}{\begin{landscape}}
  - \newcommand{\elandscape}{\end{landscape}}
  html_document:
    toc: yes
    toc_depth: '2'
    df_print: paged
---

# Abstract

@@

# H1: Nuclear Energy will be seen as riskier than other energy technologies in India.  this paper explores nuclear energy in comparison with other technologies

## Likert Responses (n= 2160)
The percentages are rounded off to whole numbers.

```{r, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
# Q1: how much is the awareness of energy technologies in India ? How does it relate to state specific data ? 
# summary of NA results from the combined sample of 2000 responses (simple percentage bar graphs)
# part 1- how much is the awareness of energy technologies in India -

#plotting perceived risk from different technologies including rather not say don't know
colorsequence<- c("#8C4646","#D9695F","#F2A679","#F2D091","#5D8C7B","#808080")

#following is the data frame for making the barplot 
df_barplot <- uncodedjoineddf %>%
  dplyr::select(starts_with("RISKY"))%>%
  gather(Technology, Perceived_Risk, Risky_Hydro:Risky_INDLPG, factor_key = TRUE)%>%
  separate(Technology, c("Risky", "Technology"), extra = "merge", fill = "left")%>%
  dplyr::select(-Risky) %>% 
  group_by(Technology, Perceived_Risk) %>%
  dplyr::summarise(n=n())

#following data frame gives us percentage for each response 
df_barplot_percent<- df_barplot%>%
  group_by(Technology) %>%
  mutate(Percentage = round(n/sum(n)*100, 0)) %>%
  ungroup()

#plotting perceived benefit from different technologies including rather not say don't know

df_barplotben <- uncodedjoineddf %>%
  dplyr::select(starts_with("Ben"))%>%
  gather(Technology, Perceived_Benefit, Ben_Hydro:Ben_INDKerosene, factor_key = TRUE)%>%
  separate(Technology, c("Ben", "Technology"), extra = "merge", fill = "left")%>%
  dplyr::select(-Ben) %>% 
  group_by(Technology, Perceived_Benefit) %>%
  dplyr::summarise(n=n())

df_barplotben_percent<- df_barplotben%>%
  group_by(Technology) %>%
  mutate(Percentage = round(n/sum(n)*100, 0)) %>%
  ungroup()

#bar plot for likert responses perceived risk - centrally owned technologies 
df_barplot %>% ggplot(aes(fill= fct_rev(factor(Perceived_Risk, levels=c("Extremely risky", "Very risky","Moderately risky","Slightly risky","Not at all risky","Rather not say/Don't know"))), y=n , x=Technology)) + 
  geom_bar(position="fill",stat="identity")+
  geom_text(data = df_barplot_percent, aes(label=paste0(Percentage, "%"), y=n), position = position_fill(vjust=0.5), size=3) +
  scale_x_discrete(limits = c("Solar", "Wind" ,"Hydro", "Oil", "Coal","Gas", "Nuclear"))+
  scale_fill_manual("legend", values = c("Extremely risky" = "#8C4646", "Very risky" = "#D9695F", "Moderately risky" = "#F2A679", "Slightly risky" = "#F2D091","Not at all risky" = "#5D8C7B", "Rather not say/Don't know" = "grey94"))+
  labs( y = "Perceived Risk", x ="Centrally Managed Energy Technologies")+
  theme_classic()

#perceived benefit centrally owned technologies

df_barplotben %>% ggplot(aes(fill= factor(Perceived_Benefit, levels=c("Rather not say/Don't know","Not at all beneficial","Slightly beneficial","Moderately beneficial","Very beneficial", "Extremely beneficial")), y=n , x=Technology)) + 
  geom_bar(position="fill",stat="identity")+
   geom_text(data = df_barplotben_percent, aes(label=paste0(Percentage, "%"), y=n), position = position_fill(vjust=0.5), size=3) +
  scale_fill_manual("legend", values = c("Rather not say/Don't know" = "grey94" ,"Not at all beneficial" = "orange","Slightly beneficial"="yellow" ,"Moderately beneficial" = "palegreen","Very beneficial"= "green3", "Extremely beneficial"= "green4"))+
  scale_x_discrete(limits = c("Solar", "Wind", "Hydro", "Oil", "Coal","Gas","Nuclear"))+
  labs( y = "Perceived Benefit", x ="Centrally Managed Energy Technologies")+
  theme_classic()

\newpage
## Introduction: Mean Perceived Risk and Mean Perceived Benefit for all energy technologies.

```{r, echo=FALSE}
library(tidyverse)

# Filter variables of interest
joineddf_subset <- joineddf %>%
  dplyr::select(!starts_with(c("Ben_IND", "Risky_IND")))%>%
  dplyr::select(starts_with("Risky"), 
         starts_with("Ben"))

# Assuming your data is named joineddf_subset
long_df <- joineddf_subset %>%
  gather(key = "Type", value = "Value")

# Separate out Risky and Ben columns
risky_df <- long_df %>% filter(str_detect(Type, "^Risky"))
ben_df <- long_df %>% filter(str_detect(Type, "^Ben"))

# Extract the technology type (Hydro, Solar, etc.)
risky_df$Tech <- str_replace(risky_df$Type, "Risky_", "")
ben_df$Tech <- str_replace(ben_df$Type, "Ben_", "")

# Calculate the mean for each technology for Risky
risky_mean <- risky_df %>%
  group_by(Tech) %>%
  dplyr::summarize(Mean_Value = mean(Value, na.rm = TRUE),
          sd = sd(Value, na.rm = TRUE),
          se = sd(Value, na.rm = TRUE) / sqrt(n()),
          .groups = "drop")

# Do the same for Ben technologies
ben_mean <- ben_df %>%
  group_by(Tech) %>%
  dplyr::summarize(Mean_Value = mean(Value, na.rm = TRUE),
          sd = sd(Value, na.rm = TRUE),
          se = sd(Value, na.rm = TRUE) / sqrt(n()),
          .groups = "drop")

# Combine the two data frames into one for plotting
combined_mean <- bind_rows(
  mutate(risky_mean, Category = "Risky"),
  mutate(ben_mean, Category = "Beneficial")
)
# Reorder the factor levels of the Tech variable by Mean_Value
risky_mean$Tech <- factor(risky_mean$Tech, levels = risky_mean$Tech[order(risky_mean$Mean_Value, decreasing = FALSE)])

```{r, echo=FALSE}
library(ggplot2)
library(gridExtra)

mean_risk <- mean(combined_mean$Mean_Value[combined_mean$Category == "Risky"], na.rm = TRUE)
mean_benefit <- mean(combined_mean$Mean_Value[combined_mean$Category == "Beneficial"], na.rm = TRUE)

# Order Technologies
technology_order <- c("Solar","Wind","Hydro","Oil","Coal", "Gas","Nuclear")
ben_mean$Tech <- factor(ben_mean$Tech, levels = technology_order)

# Generate the Ben plot with flipped y-axis
ben_plot <- ggplot(ben_mean, aes(y = Tech, x = Mean_Value)) +
  geom_bar(stat = "identity", fill = "palegreen3") +
  geom_errorbar(aes(xmin = Mean_Value - se, xmax = Mean_Value + se), width = 0.2) +
  coord_cartesian(xlim = c(5, 1)) + 
  labs(title = "Perceived Benefit", x = "Mean Values") +
  #scale_x_reverse() +
  theme(  # remove y-axis labels
        axis.title.y = element_blank()) + # remove the "Tech" axis title
  geom_vline(data = subset(combined_mean, Category == "Beneficial"), 
             aes(xintercept = mean_benefit), linetype="dotted", color = "black", size = 0.5)

# Generate the Risky plot
risky_plot <- ggplot(risky_mean, aes(y = Tech, x = Mean_Value)) +
  geom_bar(stat = "identity", fill = "firebrick2") +
  geom_errorbar(aes(xmin = Mean_Value - se, xmax = Mean_Value + se), width = 0.2) +
  coord_cartesian(xlim = c(1, 5)) + 
  labs(title = "Perceived Risk", x = "Mean Values") +
  theme(axis.text.y = element_blank(),
        axis.title.y = element_blank())+
  geom_vline(data = subset(combined_mean, Category == "Risky"), 
             aes(xintercept = mean_risk), linetype="dotted", color = "black", size = 0.5)
 # remove the "Tech" axis title

# Arrange plots side by side
grid.arrange(ben_plot, risky_plot, ncol=2)

## Boxplot for perceived benefit and perceived risk by technology

```{r, echo = FALSE, fig.width=16, fig.height=6}

#Box plot to see the distribution

# Loading the required libraries
library(tidyverse)
library(stringr)
library(gridExtra)

# Reshape the data to a long format
joineddf_subset_long <- joineddf_subset %>%
  pivot_longer(cols = everything(), 
               names_to = "variable",
               values_to = "value")

# Separate the data into two: one for "Risky_" variables and one for "Ben_" variables
risky_df <- joineddf_subset_long %>% 
  filter(str_detect(variable, "^Risky_")) %>%
  mutate(variable = str_remove(variable, "Risky_"))  # Remove the "Risky_" prefix

ben_df <- joineddf_subset_long %>% 
  filter(str_detect(variable, "^Ben_")) %>%
  mutate(variable = str_remove(variable, "Ben_"))  # Remove the "Ben_" prefix

# Remove NA values
risky_df <- risky_df %>% drop_na()
ben_df <- ben_df %>% drop_na()

# Create box plots
risky_plot <- ggplot(risky_df, aes(x = variable, y = value, fill = variable)) +
  geom_boxplot() +
  scale_fill_manual(values = rep("firebrick2", length(unique(risky_df$variable)))) +
  labs(x = "Energy Technologies", y = "Likert", fill = "Technologies") +
  ggtitle("Perceived risk") +
  theme_minimal()+
  theme(axis.text.y = element_text(size=20), 
        axis.text.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        axis.title.x = element_text(size=20),
        title = element_text(size=20))+
  guides(fill = FALSE)

ben_plot <- ggplot(ben_df, aes(x = variable, y = value, fill = variable)) +
  geom_boxplot() +
  scale_fill_manual(values = rep("palegreen3", length(unique(ben_df$variable)))) +
  labs(x = "Energy Technologies", y = "Likert Responses", fill = "Technologies") +
  ggtitle("Perceived Benefit") +
  theme_minimal()+
  theme(axis.text.y = element_text(size=20), 
        axis.text.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        axis.title.x = element_text(size=20),
        title = element_text(size=20))+
  guides(fill = FALSE)

# Put the two plots next to each other
grid.arrange(risky_plot, ben_plot, ncol = 2)

## Pairwise T-test: Mean perceived risk and mean perceived benefit (all energy technologies)

The red and green pairs indicate that there is a statistically significant difference between the means of the two groups. 
White and grey indicate - no differences between the means of the two groups.

```{r, echo = FALSE, fig.width=14, fig.height=6}
#Q2 :How are the perceptions of the risk of producing energy from nuclear fission different from that of other conventional sources of energy like coal or hydro power in India?
#H : Nuclear energy will be perceived as riskier than other sources of energy (coal or hydro) in India like in the west.
perceivedriskc <-joineddf %>% 
  dplyr::select("Risky_Solar", "Risky_Hydro", "Risky_Wind", "Risky_Nuclear", "Risky_Coal", "Risky_Gas", "Risky_Oil") %>%
  gather(key = "technology", value = "perceived_risk") %>% 
  mutate(technology = gsub("Risky_", "", technology)) %>%
  na.omit()

result_ttest <- pairwise.t.test(perceivedriskc$perceived_risk, perceivedriskc$technology, p.adjust.method = "BH")

# visualising the pairwaise t test results. the non significant pairs are grey

tidy_result_ttest <- broom::tidy(result_ttest)

heatmap1 <- ggplot(tidy_result_ttest, aes(x = group1, y = group2, fill = p.value)) + 
  geom_tile(color = "white") + 
  scale_fill_gradient2(low = "firebrick2", high = "white", midpoint = 0.025, 
                       limits = c(0, 0.05), space = "Lab", 
                       name = "P-value") + 
  theme_classic() + 
  labs(x = "", y = "") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
   theme(axis.text.y = element_text(size=20), 
        axis.text.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        axis.title.x = element_text(size=20),
        title = element_text(size=20),
        legend.text = element_text(size=12))

#Question- Why there is significant difference statistically - if the medians are the same in the boxplot.
#Q3: How do perceptions of benefit from nuclear energy compare with other source of energy?

# H : benefits from all energy technologies will be similar 
# include regression, heat maps, bar graphs? - decide which ones are good to include

perceivedbenefitc <-joineddf %>% 
  dplyr::select("Ben_Solar", "Ben_Hydro", "Ben_Wind", "Ben_Nuclear", "Ben_Coal", "Ben_Gas", "Ben_Oil") %>%
  gather(key = "technology", value = "perceived_benefit") %>% 
  mutate(technology = gsub("Ben_", "", technology)) %>%
  na.omit()

result_ttestben <- pairwise.t.test(perceivedbenefitc$perceived_benefit, perceivedbenefitc$technology, p.adjust.method = "BH")

# visualising the pairwaise t test results. the non significant pairs are grey

tidy_resultbc <- broom::tidy(result_ttestben)

library(ggplot2)
heatmap2 <- ggplot(tidy_resultbc, aes(x = group1, y = group2, fill = p.value)) + 
  geom_tile(color = "white") + 
  scale_fill_gradient2(low = "palegreen3", high = "white", midpoint = 0.025, 
                       limits = c(0, 0.05), space = "Lab", 
                       name = "P-value") + 
  theme_classic() + 
  labs(x = "", y = "") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
   theme(axis.text.y = element_text(size=20), 
        axis.text.x = element_text(size=20),
        axis.title.y = element_text(size=20),
        axis.title.x = element_text(size=20),
        title = element_text(size=20),
        legend.text = element_text(size=12))

grid.arrange(heatmap1, heatmap2, ncol=2)

## Benefit - Risk for each technology 
```{r, echo = FALSE}

# combining risk and benefit from each energy technology 
# Filter variables of interest
joineddf_subset <- joineddf %>%
  dplyr::select(!starts_with(c("Ben_IND", "Risky_IND")))%>%
  dplyr::select(starts_with("Risky"), 
         starts_with("Ben"))

acceptance <- joineddf_subset %>%
  na.omit()%>%
  mutate(Nuclear = Ben_Nuclear - Risky_Nuclear,
         Hyrdo = Ben_Hydro - Risky_Hydro,
         Wind = Ben_Wind - Risky_Wind,
         Solar = Ben_Solar - Risky_Solar,
         Coal = Ben_Coal - Risky_Coal,
         Gas = Ben_Gas - Risky_Gas,
         Oil = Ben_Oil - Risky_Oil)%>%
  dplyr::select(-starts_with(c("Risky", "Ben")))

# Plot
ggplot(mean_acceptance, aes(x = col, y = mean_val, fill = ifelse(mean_val >= 0, 'Above 0', 'Below 0'))) + 
  geom_bar(stat = "identity") +
  geom_errorbar(aes(ymin = mean_val - sem_val, ymax = mean_val + sem_val), width = 0.2) +
  geom_text(aes(label = round(mean_val, 2)), vjust = -0.9) +
  scale_fill_manual(values = c('Above 0' = 'palegreen3', 'Below 0' = 'firebrick2')) +
  labs(fill = "Legend") +
  xlab("Energy Technologies") +
  ylab("Mean Value") +
  ggtitle("Benefit- Risk for Each Energy Technology (n = 1184)") +
  theme_minimal()+
  ylim(-0.5, 1.75)

# Claim 1: Demographic variables: nuclear, solar, coal

# # Convert `caste` into binary variable 'upper' (1) vs 'non-upper' (0)
joineddf$Uppercaste <- ifelse(joineddf$caste %in% c('Brahmin', 'General'), 1, 0)
# Convert `gender` into binary variable 'male' (1) vs 'female' (0)
joineddf$Male <- ifelse(joineddf$gender == 'Male', 1, 0)
# Convert `religion` into binary variable 'Hinduism' (1) vs 'Non-Hinduism' (0)
joineddf$Hindu <- ifelse(joineddf$religion == 'Hinduism', 1, 0)
codedmodule2$State <- as.factor(codedmodule2$State)
codedmodule2$gender <- as.factor(codedmodule2$gender)
codedmodule2$Urban <- as.factor(codedmodule2$urban_rural)
joineddf$Urban <- as.factor(joineddf$urban_rural)
codedmodule2$caste <- as.factor(codedmodule2$caste)
codedmodule2$religion <- as.factor(codedmodule2$religion)
# # Convert `caste` into binary variable 'upper' (1) vs 'non-upper' (0)
codedmodule2$Uppercaste <- ifelse(codedmodule2$caste %in% c('Brahmin', 'General'), 1, 0)
# Convert `gender` into binary variable 'male' (1) vs 'female' (0)
codedmodule2$Male <- ifelse(codedmodule2$gender == 'Male', 1, 0)
# Convert `religion` into binary variable 'Hinduism' (1) vs 'Non-Hinduism' (0)
codedmodule2$Hindu <- ifelse(codedmodule2$religion == 'Hinduism', 1, 0)

joineddf1 <- joineddf %>%
            dplyr::select(Risky_Nuclear, Risky_Solar, Risky_Coal, Uppercaste, Male, Hindu, Urban, age, State) %>%
            na.omit()

# lm on nuclear energy with all demovars

alldemos <- joineddf1 %>%
            dplyr::select(Risky_Nuclear, Uppercaste, Male, Hindu, Urban, age, State) %>%
            mutate(RiskNuclear = Risky_Nuclear)%>%
  mutate_at(vars(age), funs(case_when(. == "18-24 years old" ~ 1, 
                                      . == "25-34 years old" ~ 2,
                                      . ==  "35-44 years old" ~3,
                                      . == "45-54 years old" ~ 4,
                                      . == "55-64 years old" ~ 5,
                                      . == "65-74 years old" ~ 6,
                                      . == "75 years or older" ~ 7)))

alldemoslm1 <- lm(RiskNuclear ~ Uppercaste + Male + Hindu + Urban + age , data = alldemos)

alldemoslm2<- lm(RiskNuclear ~ Uppercaste + Male + Hindu + Urban + age + State, data = alldemos)

#lm on solar with all demovars

salldemos <- joineddf1 %>%
            dplyr::select(Risky_Solar,Uppercaste, Male, Hindu, Urban, age, State)%>%
            mutate(RiskSolar = Risky_Solar)%>%
  mutate_at(vars(age), funs(case_when(. == "18-24 years old" ~ 1, 
                                      . == "25-34 years old" ~ 2,
                                      . ==  "35-44 years old" ~3,
                                      . == "45-54 years old" ~ 4,
                                      . == "55-64 years old" ~ 5,
                                      . == "65-74 years old" ~ 6,
                                      . == "75 years or older" ~ 7)))

salldemoslm1 <- lm(RiskSolar ~ Uppercaste + Male + Hindu + Urban + age , data = salldemos)

salldemoslm2<- lm(RiskSolar ~ Uppercaste + Male + Hindu + Urban + age + State, data = salldemos)

#lm on coal with all demovars 
calldemos <- joineddf1 %>%
            dplyr::select(Risky_Coal,Uppercaste, Male, Hindu, Urban, age, State)%>%
            mutate(RiskCoal = Risky_Coal)%>%
            mutate_at(vars(age), funs(case_when(. == "18-24 years old" ~ 1, 
                                      . == "25-34 years old" ~ 2,
                                      . ==  "35-44 years old" ~3,
                                      . == "45-54 years old" ~ 4,
                                      . == "55-64 years old" ~ 5,
                                      . == "65-74 years old" ~ 6,
                                      . == "75 years or older" ~ 7)))

calldemoslm1 <- lm(RiskCoal ~ Uppercaste + Male + Hindu + Urban + age, data = calldemos)

calldemoslm2<- lm(RiskCoal ~ Uppercaste + Male + Hindu + Urban + age + State, data = calldemos)

# trying linear regression with acceptance scale

joineddf_subset1 <- joineddf %>%
  dplyr::select(!starts_with(c("Ben_IND", "Risky_IND")))%>%
  dplyr::select(starts_with("Risky"), 
         starts_with("Ben"), Uppercaste, Male, Hindu, Urban, age)

acceptance1 <- joineddf_subset1 %>%
  na.omit()%>%
  mutate(NetBenNuclear = Ben_Nuclear - Risky_Nuclear,
         NetBeneHyrdo = Ben_Hydro - Risky_Hydro,
         NetBeneWind = Ben_Wind - Risky_Wind,
         NetBenSolar = Ben_Solar - Risky_Solar,
         NetBenCoal = Ben_Coal - Risky_Coal,
         NetBenGas = Ben_Gas - Risky_Gas,
         NetBenOil = Ben_Oil - Risky_Oil)%>%
  dplyr::select(-starts_with(c("Risky", "Ben")))%>%
  mutate_at(vars(age), funs(case_when(. == "18-24 years old" ~ 1, 
                                      . == "25-34 years old" ~ 2,
                                      . ==  "35-44 years old" ~3,
                                      . == "45-54 years old" ~ 4,
                                      . == "55-64 years old" ~ 5,
                                      . == "65-74 years old" ~ 6,
                                      . == "75 years or older" ~ 7)))

alldemoslm3<- lm(NetBenNuclear ~ Uppercaste + Male + Hindu + Urban + age, data = acceptance1)
#summary(alldemoslm3)

salldemoslm3<- lm(NetBenSolar ~ Uppercaste + Male + Hindu + Urban + age, data = acceptance1)
calldemoslm3<- lm(NetBenCoal ~ Uppercaste + Male + Hindu + Urban + age, data = acceptance1)

\blandscape

## Linear Regression with demographic variables (caste, religion, gender and age)

cat("\\begingroup")
cat("\\small")  # Adjusts the font size
cat("\\setlength{\\tabcolsep}{1pt}")
cat("\\renewcommand{\\arraystretch}{0.7}")
stargazer(alldemoslm1, salldemoslm1, calldemoslm1,alldemoslm3, salldemoslm3, calldemoslm3,
          title = "Linear Models: Perceived Risk and Net Perceived Benefit(Nuclear, Solar and Coal)",
          type = "latex"
)
cat("\\endgroup")

\elandscape

stargazer(alldemoslm1, salldemoslm1, calldemoslm1, alldemoslm3, salldemoslm3, calldemoslm3, 
          type = "text", # Choose "html" or "latex" for different formats
          title = "Regression Models Summary",
          align = TRUE)

# Claim 2: Regional differences

@@

```
## Radar chart - risk and benefit by state

```{r, echo=FALSE}
library(tidyverse)

# Filter variables of interest
joineddf_subset2 <- joineddf %>%
  dplyr::select(!starts_with(c("Ben_IND", "Risky_IND")))%>%
  dplyr::select(starts_with("Risky"), 
         starts_with("Ben"), starts_with("State"))

#long_df2 <- joineddf_subset %>%
#gather(key = "Type", value = "Value")
# Reshape data to long format
long_df2 <- joineddf_subset2 %>%
  pivot_longer(cols = -State, names_to = "variable", values_to = "value")

# Separate out Risky and Ben columns
risky_df2 <- long_df2 %>% filter(str_detect(variable, "^Risky"))
ben_df2 <- long_df2 %>% filter(str_detect(variable, "^Ben"))

# Extract the technology type (Hydro, Solar, etc.)
risky_df2$Tech <- str_replace(risky_df2$variable, "Risky_", "")
ben_df2$Tech <- str_replace(ben_df2$variable, "Ben_", "")

# Calculate the mean for each technology for Risky
risky_mean2 <- risky_df2 %>%
  group_by(State,Tech) %>%
  dplyr::summarize(Mean_Value = mean(value, na.rm = TRUE),
          sd = sd(value, na.rm = TRUE),
          se = sd(value, na.rm = TRUE) / sqrt(n()),
          .groups = "drop")

# Do the same for Ben technologies
ben_mean2 <- ben_df2 %>%
  group_by(State,Tech) %>%
  dplyr::summarize(Mean_Value = mean(value, na.rm = TRUE),
          sd = sd(value, na.rm = TRUE),
          se = sd(value, na.rm = TRUE) / sqrt(n()),
          .groups = "drop")

# Combine the two data frames into one for plotting
combined_mean2 <- bind_rows(
  mutate(risky_mean2, Category = "Risky"),
  mutate(ben_mean2, Category = "Beneficial")
)

# New order of technologies
new_tech_order <- c("Solar", "Wind", "Hydro", "Oil", "Coal", "Gas","Nuclear")

# Apply this new order to the 'Tech' column in your combined_mean dataset
combined_mean2$Tech <- factor(combined_mean2$Tech, levels = new_tech_order)

# Split the data by state
data_by_state <- split(combined_mean2, combined_mean2$State)

@@

```{r, echo=FALSE}
# Create a list to store plots
plots_list <- list()

for (state in names(data_by_state)) {
  # Subset data for each state
  state_data <- data_by_state[[state]]

  # Split into beneficial and risky data
  ben_mean <- subset(state_data, Category == "Beneficial")
  risky_mean <- subset(state_data, Category == "Risky")

  # Generate plots for each category
  ben_plot <- ggplot(ben_mean, aes(y = Tech, x = Mean_Value)) +
    geom_bar(stat = "identity", fill = "palegreen3") +
    geom_errorbar(aes(xmin = Mean_Value - se, xmax = Mean_Value + se), width = 0.2) +
    coord_cartesian(xlim = c(5, 1)) + 
    labs(title = paste("Perceived Benefit in", state), x = "Mean Values") +
    theme(axis.title.y = element_blank()) +
    geom_vline(xintercept = mean_benefit, linetype="dotted", color = "black", size = 0.5)

  risky_plot <- ggplot(risky_mean, aes(y = Tech, x = Mean_Value)) +
    geom_bar(stat = "identity", fill = "firebrick2") +
    geom_errorbar(aes(xmin = Mean_Value - se, xmax = Mean_Value + se), width = 0.2) +
    coord_cartesian(xlim = c(1, 5)) + 
    labs(title = paste("Perceived Risk in", state), x = "Mean Values") +
    theme(axis.text.y = element_blank(), axis.title.y = element_blank())+
    geom_vline(xintercept = mean_risk, linetype="dotted", color = "black", size = 0.5)

  # Combine the plots side by side
  combined_plot <- grid.arrange(ben_plot, risky_plot, ncol=2)
  plots_list[[state]] <- combined_plot
}

## Net benefit by state

```{r, echo=FALSE}
library(dplyr)
library(ggplot2)

# Including the State variable in the dataset
joineddf_subset_state <- joineddf %>%
  dplyr::select(starts_with("Risky"), 
         starts_with("Ben"), 
         State)

acceptance_state <- joineddf_subset_state %>%
  na.omit() %>%
  mutate(Nuclear = Ben_Nuclear - Risky_Nuclear,
         Hydro = Ben_Hydro - Risky_Hydro,
         Wind = Ben_Wind - Risky_Wind,
         Solar = Ben_Solar - Risky_Solar,
         Coal = Ben_Coal - Risky_Coal,
         Gas = Ben_Gas - Risky_Gas,
         Oil = Ben_Oil - Risky_Oil) %>%
  dplyr::select(-starts_with(c("Risky", "Ben")))

# Calculate mean and standard error for each state and technology
mean_acceptance_state <- acceptance_state %>%
  group_by(State) %>%
  summarise(across(Nuclear:Oil, list(mean = ~mean(., na.rm = TRUE), 
                                     sem = ~sqrt(var(., na.rm = TRUE) / length(na.omit(.))))))

# Reshape data for plotting
long_mean <- mean_acceptance_state %>%
  pivot_longer(cols = -State, names_to = "Technology_SEM", values_to = "mean_val") %>%
  separate(Technology_SEM, into = c("Technology", "Metric"), sep = "_") %>%
  filter(Metric == "mean") %>%
  select(-Metric)

long_sem <- mean_acceptance_state %>%
  pivot_longer(cols = -State, names_to = "Technology_SEM", values_to = "sem_val") %>%
  separate(Technology_SEM, into = c("Technology", "Metric"), sep = "_") %>%
  filter(Metric == "sem") %>%
  select(-Metric)

# Merge mean and SEM data
plot_data <- left_join(long_mean, long_sem, by = c("State", "Technology"))

# Create the plot
ggplot(plot_data, aes(x = Technology, y = mean_val, fill = ifelse(mean_val >= 0, 'Above 0', 'Below 0'))) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = mean_val - sem_val, ymax = mean_val + sem_val), 
                position = position_dodge(), width = 0.25) +
  facet_wrap(~ State) +
  scale_fill_manual(values = c('Above 0' = 'palegreen3', 'Below 0' = 'firebrick2')) +
  labs(title = "Net Benefit (Perceived Risk - Perceived Benefit) by State",
       x = "Energy Technologies", y = "Net Benefit", fill = "Legend") +
  theme_minimal() +
  ylim(-1.75, 3.5)

staterisky <- joineddf %>%
  dplyr::select(!starts_with(c("Ben_IND", "Risky_IND")))%>%
  dplyr::select(starts_with("Risky"), State)

@@

@@

# Order Technologies
technology_order <- c("Coal", "Gas", "Nuclear", "Oil", "Hydro", "Wind", "Solar")
long_data$Technology <- factor(long_data$Technology, levels = technology_order)

cbbPalette <- c("#000000","#CC79A7","#F0E442","#E69F00","#56B4E9","#009E73","#D55E00")

names(cbbPalette) <- technology_order

# Order States (assuming you want an alphabetical order, modify as needed)
states_order <- c( "Rajasthan", "Maharashtra", "Tamil Nadu", "Uttar Pradesh",  "West Bengal")
long_data$State <- factor(long_data$State, levels = states_order)

# Plot the graph
stateplot1 <- ggplot(long_data, aes(x = State, y = Mean_Score, color = Technology, group = Technology)) +
  geom_line(size = 0.7) +
  geom_point(size = 2) +
  labs(title = " ",
       x = "State", y = "Means") +
  ylim(1,5)+
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_color_manual(values=cbbPalette)

@@

```{r, echo= FALSE}

# Reshape the data from wide to long format
staterisky_long <- staterisky %>%
  pivot_longer(
    cols = starts_with("Risky_"),
    names_to = "Technology",
    values_to = "Riskiness"
  ) %>%
  mutate(Technology = sub("Risky_", "", Technology))

# Calculate the sample size for each state

state_sample_size <- staterisky %>%
  group_by(State) %>%
  summarize(n = n())

# Join this back to the main data frame
staterisky_long <- staterisky_long %>%
  left_join(state_sample_size, by = "State")

# Calculate the weighted mean for each technology in each state
weighted_means <- staterisky_long %>%
  group_by(State, Technology) %>%
  summarize(weighted_mean = sum(Riskiness / n, na.rm = TRUE) / sum(1 / n, na.rm = TRUE), .groups = 'drop')

@@

weighted_means$Technology <- factor(weighted_means$Technology, levels = technology_order)
states_order <- c( "Rajasthan", "Maharashtra", "Tamil Nadu", "Uttar Pradesh",  "West Bengal")
weighted_means$State <- factor(weighted_means$State, levels = states_order)

stateplot2 <- ggplot(weighted_means, aes(x = State, y = weighted_mean, color = Technology, group = Technology)) +
  geom_line(size = 0.7) +
  geom_point(size = 2) +
  labs(title = " ",
       x = "State", y = "Weighted Means") +
  ylim(0.5,4.5)+
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_manual(values = cbbPalette)

\newpage 
## Mean Perceived Risk and Weighted Mean

```{r, echo=FALSE, fig.width=8, fig.height=4,out.width='100%', out.height='100%'}
library(gridExtra)
# mean perceived risk and zscores by state side by side

spacer <- grid::rectGrob(gp = grid::gpar(col = "white"))

grid.arrange(stateplot1, spacer, stateplot2, ncol=3, widths=c(0.8, 0.06, 0.8))
```

\newpage
## Mean Perceived risk and weighten means by Technologies- solar, coal and nuclear

staterisky3t <- joineddf %>%
  dplyr::select(!starts_with(c("Ben_IND", "Risky_IND")))%>%
  dplyr::select(Risky_Solar, Risky_Nuclear, Risky_Coal, State)

staterisky3t_mean <- staterisky3t %>%
  group_by(State) %>%
  summarise(
    Mean_Risky_Solar = mean(Risky_Solar, na.rm = TRUE),
    Mean_Risky_Nuclear = mean(Risky_Nuclear, na.rm = TRUE),
    Mean_Risky_Coal = mean(Risky_Coal, na.rm = TRUE)
  )

# Convert to long format
long_data3t <- staterisky3t_mean %>%
  gather(Technology, Mean_Score, -State) %>%
  mutate(Technology = gsub("Mean_Risky_", "", Technology))

# Order Technologies
technology_order <- c("Coal", "Gas", "Nuclear", "Oil", "Hydro", "Wind", "Solar")
long_data3t$Technology <- factor(long_data3t$Technology, levels = technology_order)
